---
title: "Zooplankton graphic"
description: |
  Data Sciences I
author:
  - name: Massart Théo
    url: {}
date: 11-13-2020
categories:
  - "SDD"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup}
SciViews::R
```

```{r importation}
# Importation du jeu de données
zooplankton <- read(file = "zooplankton", package = "data.io", lang = "fr")
names(zooplankton)
```

These data are various features measured by image analysis of zooplankton originating from Tulear, Madagascar. This topic will show us the size distribution of zooplankton according to their taxonomic classification. 

```{r graphe}
library(ggridges)
 chart(zooplankton, class ~ size %fill=% class) +
  geom_density_ridges(orientation = "y", show.legend = FALSE) +
   xlab("Height [mm]") +
   ylab("Classification")
 
```
On this graphic we can see that zooplankton are really small. They are less than 2 millimeters high except for Chaetognath and Cnidarian. These two classes have various sizes ranging from 0 to 6 millimeters.


